---
title: "Inside TicTacJoe"
output: html_notebook
---
Load the needed objects, representing the game
```{r}
# Load precomputed game setup
PrecomputedFilesLocation = "precomputed_state"
load(file=file.path(PrecomputedFilesLocation, "States.RData"))
load(file=file.path(PrecomputedFilesLocation, "StopStates.RData"))
load(file=file.path(PrecomputedFilesLocation, "LinkedStates.RData"))
load(file=file.path(PrecomputedFilesLocation, "ProbStates.RData"))
```

## States

`States` stores all possible board configurations up to symmetry. There are 9 moves at most, so together with initial empty board, that gives 10 levels of states.
```{r}
length(States)
```
The first level is an empty board
```{r}
States[[1]]
```
The first move can be placed in only 3 places (corner, middle of border, center of board), when reduced with respect to symmetry
```{r}
States[[2]]
```
Note, that the logic here is that the 9 values store positions from top-left corner, top-middle, top-right corner, middle-left...

The moves of the second player are denoted with a `2`, hence
```{r}
States[[7]][[56]]
```
To visualize what board states is coded by this state, let us prepare a function
```{r}
print_board = function(state) {
  print(t(matrix(state, sqrt(length(state)))))
}

print_board(States[[7]][[56]])
```

The number of possible board configurations (reduced with symmetry) is
```{r}
for(i in 1:10){print(length(States[[i]]))}
```

## ProbStates

`ProbStates` holds the probabilities with which TicTacJoe makes a given move. This is TicTacJoe's understanding of the game or its brain. `ProbStates` are initialized with uniform distribuitions, meaning in each board configuration, all the moves are equally probable, e.g., all three first moves are equally likely
```{r}
ProbStates[[1]]
```
While there is a level in `ProbStates` for every level in `States`,
```{r}
for(i in 1:10){print(length(ProbStates[[i]]))}
```
The length of levels vectors on a level depend on how many options there are.

As the training of TicTacJoe progresses, the ProbStates are updated, eventually saturating on probabilities being close to one-hot vectors, e.g., `[0, 0, 1, 0]`.

## StopStates

The `StopStates` stores information about which player won in a given state (or if there is no winner). It has the same structure as `States`
```{r}
for(i in 1:10){print(length(StopStates[[i]]))}
```

Let us verify if the state we used above is indeed marked as a win for player number `2`
```{r}
print_board(States[[7]][[56]])

print(paste("Stop state for this state of board is:", StopStates[[7]][[56]]))
```

## LinkedStates

`LinkedStates` holds information of the indexes of the states following a given state under a choice coded by `ProbStates`. They have the same level structure as `States`
```{r}
for(i in 1:10){print(length(LinkedStates[[i]]))}
```

To see how it works, let us take the state of the board considered above
```{r}
state_level <- 7
board_config <- 56

print_board(States[[state_level]][[board_config]])
```

Let us consider state `States[[6]][[25]]`
```{r}
print_board(States[[6]][[25]])
```
It is now a move of player `2` and they have 4 options (no symmetries apply), hence
```{r}
length(ProbStates[[6]][[25]]) == length(LinkedStates[[6]][[25]])
length(ProbStates[[6]][[25]]) == 4
```
The four possible next board states are
```{r}
for(i in 1:length(LinkedStates[[6]][[25]])) {
  print_board(States[[7]][[LinkedStates[[6]][[25]][[i]]]])
}
```
Note, that some of the boards may be rotated or flipped.
```{r}
# LinkedStates[[6]][[25]]
States[[7]][[41]]
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
